NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-12-05 RefereeReply1.txt

We would like to thank the referee for his/her constructive and valuable 
comments.  The points raised clearly helped us to further improve the 
quality of the manuscript.  Below we give detailed replies to the referee's 
queries and indicate the corresponding adjustments or additions to the 
manuscript.  We thereby follow the referee's initial ordering: 
1) 
2)
3)
4)
5)
6)
7)
8)  The figure captions have been corrected.
9)  This has been rephrased to clearly state which particles the invariant 
    mass cut acts on.
10) The PDFs have been specified, and the respective publication referenced.
11) 
12) The description of the observables has been enhanced in the following 
    cases:
    - 
    - 
13) We agree and added a sentence stating exactly that.

We again would like to thank for the his/her feedback that clearly helped us to 
further improve the quality of the paper. We hope to have addressed all raised 
questions and suggestions such that the paper in its present form can be 
published in JHEP.

Sincerely yours

Nicolas Greiner, Marek Schoenherr

### 2017-12-05 results.tex
corrections for points 8, 9, 10, 11 and 13 of referee report, added draft reply

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_l1}
  \caption{
    Transverse momentum of the leading (left), subleading (centre) 
    and third leading (right) photon at the LHC at 13\,TeV.
    \label{fig:aaw:pt}
  }
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1y2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1l1_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_t_comb_log}
  \caption{
    Pairwise invariant mass of the leading and subleading photon (left),
    leading and third leading photon (centre), subleading and third leading 
    photon (right) at the LHC at 13\,TeV.
    \label{fig:aaw:myy}
  }
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_l1}
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y2_l1}
  \caption{
    Azimuthal separation of the leading and subleading photon (left),
    leading and third leading photon (centre), subleading and third leading 
    photon (right) at the LHC at 13\,TeV.
    \label{fig:aaw:dphi}
  }
\end{figure}

@@

Finally, we consider diphoton production in association with 
a $Z$ boson in its leptonic decay channel. 
In practise we look at lepton pair production including 
all non-resonant diagrams.
The fiducial phase space of our analysis is defined as follows, again according 
to existing measurements \cite{Aad:2016sau}. 
First, we require the presence of exactly one lepton pair 
of opposite charge, dressed with all photons in a cone of 
size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
Their invariant mass must be larger than 40\,GeV. 
As in the case of \aaw production, we then require at least 
two identified photons among the remaining ones after dressing, 
using the procedure described in Sec.\ \ref{sec:results:aaa}, 
loosening the transverse momentum requirements to 
$\pT>15\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
the lepton to be $\Delta R(\ell,\gamma)>0.4$.
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.

@@

Finally, \aaz\ production is the only process of the three processes 
considered in this publication which can be produced through 
photon-induced channels at leading order, 
$\gamma\gamma\to\ell^+\ell^-\gamma\gamma$. 
To this end, we investigate their contribution at LO in 
Figure \ref{fig:aaz:aa-ind}. 
The photon-induced contribution is typically a few per mille of the 
LO cross section, but raises up to 2\% for invariant masses larger 
than 1\,TeV, especially $m_{\gamma_i\ell^+\ell^-}$. 
In this region, however, typical QCD and EW corrections are much larger 
such that this contribution can be safely ignored. 
As the photon-induced processes only contribute through non-resonant 
lepton-pair production, their contribution can be further suppressed 
by tightening the acceptance window in the lepton-pair invariant mass.

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_y1}
  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaw/pT_l1}
  \caption{
    Transverse momentum of the leading (left) and subleading (centre) 
    photon as well as the dressed lepton (right) in diphoton production 
    in association with a lepton-neutrino pair at the LHC at 13\,TeV. 
    Details as in Fig.\ \ref{fig:aaa:pt}.
    \label{fig:aaw:pt}
  }
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1y2_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_y1l1_comb_log}
  \includegraphics[width=0.32\textwidth]{figs_aaw/m_t_comb_log}
  \caption{
    Pairwise invariant mass of the leading and subleading photon (left),
    the leading photon and the dressed lepton (centre), and the 
    transverse mass of the $W$ boson (right)
    in diphoton production in association with a lepton-neutrino 
    pair at the LHC at 13\,TeV. 
    Details as in Fig.\ \ref{fig:aaa:pt}.
    \label{fig:aaw:myy}
  }
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_y2}
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y1_l1}
  \includegraphics[width=0.32\textwidth]{figs_aaw/dphi_y2_l1}
  \caption{
    Azimuthal separation of the leading and subleading photon (left),
    the leading photon and the dressed lepton (centre), and the subleading 
    photon and the dressed lepton (right)
    in diphoton production in association with a lepton-neutrino pair 
    at the LHC at 13\,TeV. 
    Details as in Fig.\ \ref{fig:aaa:pt}.
    \label{fig:aaw:dphi}
  }
\end{figure}

@@

Finally, we consider diphoton production in association with 
a $Z$ boson in its leptonic decay channel. 
In practise we look at lepton pair production including 
all non-resonant diagrams.
The fiducial phase space of our analysis is defined as follows, again according 
to existing measurements \cite{Aad:2016sau}. 
First, we require the presence of exactly one lepton pair 
of opposite charge, dressed with all photons in a cone of 
size $R=0.1$, with $\pT>20\,\text{GeV}$ and $|\eta|<2.47$. 
The dressed lepton pair invariant mass must be larger than 40\,GeV. 
As in the case of \aaw production, we then require at least 
two identified photons among the remaining ones after dressing, 
using the procedure described in Sec.\ \ref{sec:results:aaa}, 
loosening the transverse momentum requirements to 
$\pT>15\,\text{GeV}$ for both the leading and the subleading 
identified photon. 
We further demand the angular separation of both photons 
to be $\Delta R(\gamma_1,\gamma_2)>0.4$ and each photon and 
each lepton to be $\Delta R(\ell,\gamma)>0.4$.
The inclusive cross sections and correction factors were 
detailed in Tab.\ \ref{tab:xsec}.

@@

Finally, \aaz\ production is the only process of the three processes 
considered in this publication which can be produced through 
photon-induced channels at leading order, 
$\gamma\gamma\to\ell^+\ell^-\gamma\gamma$. 
To this end, we investigate their contribution at LO in 
Figure \ref{fig:aaz:aa-ind}. 
\revised{To ensure that the quark and gluon PDFs are as close as 
possible to our nominal set, they are calculated using the CT14nlo 
QED \cite{Schmidt:2015zda} set, including both an elastic and an 
inelastic (with an intrinsic photon momentum fraction of 
$p_0^\gamma=0.005$) component.}
The photon-induced contribution is typically a few per mille of the 
LO cross section, but raises up to 2\% for invariant masses larger 
than 1\,TeV, especially $m_{\gamma_i\ell^+\ell^-}$. 
In this region, however, typical QCD and EW corrections are much larger 
such that this contribution can be safely ignored. 
As the photon-induced processes only contribute through non-resonant 
lepton-pair production, their contribution can be further suppressed 
by tightening the acceptance window in the lepton-pair invariant mass.
\revised{Following \cite{Denner:2015fca}, the $\gamma q$- and 
$\gamma\bar{q}$-induced channels at NLO EW are expected to contribute 
less than the $\gamma\gamma$ channels, both with and without a jet veto. 
They can thus be safely neglected here as well. 
The same reasoning also applies to \aaw\ production, 
cf.\ \cite{Denner:2014bna}.}
